FoRTE baseline

### 2019-03-27 analysis/paper/paper.Rmd
Minor outline revision

@@

```{r lai_10yr, fig.cap = lai_10yr_cap, fig.dim = c(10, 7)}
readd(results_plot)
```

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
readd(rad_lineplot)
```

>>>>

```{r lai_10yr, fig.cap = lai_10yr_cap, fig.dim = c(10, 7)}
readd(results_plot)
```
`r lai_10yr_cap`

@@

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
readd(rad_lineplot)
```
`r rad_barplot_cap`
